---
title: "Computing IBI Series"
author: "Daniel N. Albohn"
date: "11/08/2017"
output: 
  html_document:
    theme: cosmo
    css: style.css
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, error = FALSE, eval = FALSE)
```

# Preparing file for IBI extraction
We are going to use the `physioscripts` suite of functions to use peak signal detection
and compute the IBI series. In order to use the built-in signal detection utilities in
this suite of functions, each participant needs a few additional files to tell the program
how to handle the raw data. The `phys_file()` and `phys_info()` functions helper functions
I wrote to put the raw ECG signal into a format that the automatic R peak detection
algorithm (from the `physioscripts` package) is expecting.

```{r prep_ibi, eval = FALSE}
source('R/hrv_tutorial/physio_functions.R')

df <- readRDS(data, file = 'data/hrv_tutorial/sub1101a.RDS')

# create and write each new ecg file and event file
phys_file(df, c('time','ecg'), 'data/hrv_tutorial/sub1101')
phys_info('sub1101', 'data/hrv_tutorial/', fs = 1000, origin = NA)
```

Now, we can pass the `.phys.csv` file to the process and extract functions.

```{r}
files <- list.files('data/hrv_tutorial/', pattern = 'phys.csv', full.names = TRUE)

process.ecg(in.file.list = files, processing.mode = "batch")

extract.ibi(in.file.list = files, processing.mode = "batch")
```

Let's take a look at the ibi file that was created:

```{r eval=TRUE}
head(read.csv('data/hrv_tutorial/sub1101.phys.csv'))

head(read.csv('data/hrv_tutorial/sub1101.ibi.gz'))
```



