---
title: "Analyzing HRV Data in R"
author: "Daniel N. Albohn"
date: "11/08/2017"
output: 
  html_document:
    theme: cosmo
    css: style.css
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, error = FALSE)
```

In preparation. Check back soon...

# Preperation

This tutorial will use the [`RHRV`](http://rhrv.r-forge.r-project.org) package for the
majority of analyses and graphing.
In addition, it will supplement these with custom functions (which can be found on the GitHub),
and scripts from [`PhysioScript`](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3767411/).
In general, this tutorial also attempts to follow the principles of tidy data,
and will utilize various functions and
ideas from the `tidyverse` group of packages.

First, download a copy of the [zipped project]().
Then, load all of the necessary packages into your session.

```{r}

check <- require(pacman)
if(check==FALSE) {install.packages('pacman')} else(rm(check))

pacman::p_load(RHRV, tidyverse, here)

```

Next, you can load the `PhysioScript` functions by using `load()`.

```{r}

here()
load(here('R/hrv_tutorial/PhysioScript.RData'))

```

You can then examine what each of these functions do by clicking on them. If you
have the desire to clean your Global Environment you can remove all of the functions
by running the command `rm(list=ls())`.

```{r}

rm(list= ls()[!(ls() %in% c('process.ecg','extract.ibi'))])

```


## Tutorial Overview

1). Extracting electrophysiology data from raw files

2). Prepare files and compute interbeat interval

3). Check for outliers and graph

4). Obtain statistics

5). Dealing with triggers

6). Graphing






