---
title: "Using Shiny for Research"
author: "Daniel N. Albohn"
date: "12/06/2017"
output: 
  html_document:
    theme: cosmo
    css: style.css
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
```

# Overview
This group of tutorials is meant to be a *brief* and *gentle* introduction to `shiny`.

Fair warning: If you have experience with the `shiny` package or any web development,
this tutorial is probably not for you. Rstudio has several more advanced topics for
programming with shiny. In addition, [Dean Attali](https://github.com/daattali/advanced-shiny)
has a nice curated list of shiny topics. Check out the [resources page](beyond_hello.html)
for more info.

## What is this "Shiny" you speak of?
`shiny` is an `R` package by RStudio that allows for the creation of interactive "web apps".
Web apps is quoted because shiny apps need not be deployed on the web, nor do they have to be
"apps" in the sense that they require some interactive/reactive content.

A shiny app written using shiny syntax is really just a wrapper around a lot of HTML, CSS,
and JavaScript code. The benefit to using the `shiny` package as opposed to standalone
HTML is two-fold: First, the shiny syntax should be (more) familiar to long-term `R` users,
and two, it is relatively easy and plays nicely with `R`.

Even if you know HTML, JavaScript, or CSS, the raw power of these programming languages
can easily be incorporated into a shiny application. We will see some very basic HTML
code in this tutorial, but for more integration check out the page on
[extending](beyond_hello.html) shiny beyond this introduction.

# Preparation
Throughout this tutorial we will be using several core packages to build
each of the applications. You can check to see if you already have them
downloaded, and if not install them by running the code below:

```{r}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, shiny, shinyjs)
```

The code checks to see if the package `pacman` is installed, and if not,
installs it. `pacman` is a useful package manager/loader that quickly
checks if a package is installed, installs it if need be, and then loads it.

The main packages we are going to deal with are:

- `shiny`: the base package, from which most of the shiny architecture
is built on.

- `shinyjs`: A JavaScript library for shiny; allows for some more complex
functions and additions to shiny.

Feel free to clone the whole site repo on [GitHub](https://github.com/d-bohn/tutorials),
or download a standalone [zip file](https://psu.box.com/s/xsevf3t7e43sz4ry9mttrnqjqk0k48hz)
with all of the necessary code.

# Table of Contents

1). Hello, shiny!

  - [Part I](hello_shiny.html) - Basic shiny components
  - [Part II](hello_shinyII.html) - Making my first app a bit more personal

2). Hello, interactive applications! - A simple user file input, summary output app

  - [Intermediate example](io_app.html)
    
3). Hello, survey! - Creating a simple survey in shiny
    
  - [Example](simple_shiny_survey.html)

3). [Beyond a simple introduction](beyond_hello.html)

