---
title: "Using Shiny for Research"
author: "Daniel N. Albohn"
date: "12/06/2017"
output: 
  html_document:
    theme: cosmo
    css: style.css
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Overview

## What is this Shiny you speak of?

# Preparation

Throughout this tutorial, we will be using several core packagesto build
each of the applications. You can check to see if you already have them
downloaded, and if not install them by running the code below:

```{r}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, shiny, shinyjs)
```

The code checks to see if the package `pacman` is installed, and if not,
installs it. `pacman` is a useful package manager/loader that quickly
checks if a package is installed, installs it if need be, and then loads it.

The main packages we are going to deal with are:

- `shiny`: the base package, from which most of the shiny architecture
is built on.

- `shinyjs`: A Javascript library for shiny; allows for some more complex
functions and additions to shiny.

# Table of Contents

1). Hello, Shiny!
    - [Part I](hello_shiny.html) - Basic shiny components
    - [Part II](hello_shinyII.html) - Making my first app a bit more personal

2). Hello, interactive programming! - A simple user file input, summary output app

3). Hello, survey! - Creating and distrbuting surveys in Shiny

4). Beyond a simple introduction

